\documentclass[12pt,a4paper]{article}

\usepackage[margin=0.25in]{geometry}

\usepackage{enumitem}

\usepackage{hyperref}

\usepackage{multicol}

\usepackage{titlesec}

\usepackage{fontawesome5}

\usepackage{setspace}
\onehalfspacing  % 1.5 line spacing

\pagenumbering{gobble}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

%--------------------%
%     Header         %
%--------------------%
\begin{center}
    {\LARGE \textbf{Hassnain Ali}}\\
    \href{tel:+923103593706}{\faPhone~+92-310-3593706} \quad
    \href{mailto:hassnainalidayo6@gmail.com}{\faEnvelope~hassnainalidayo6@gmail.com} \quad
    {\faMapMarker~Jamshoro} \quad
    \href{https://www.linkedin.com/in/hassnain-ali-dayo-16984923b/}{\faLinkedin~LinkedIn} \quad
    \href{https://github.com/hassnain0}{\faGithub~GitHub}
\end{center}

%--------------------%
%  Executive Summary %
%--------------------%
\section*{Executive Summary}
I have total 3 years of experience in Full Stack Development, specializing in React Native, React, and Node.js. Proficient in building responsive mobile and web applications, implementing RESTful APIs, and deploying applications on AWS cloud infrastructure. Skilled in React Native, JavaScript, TypeScript, Redux, Node.js, Express, Firebase, Supabase, AWS (EC2, S3, Lambda, API Gateway), and DevOps practices. Experienced in building scalable backend systems, managing server infrastructure, and implementing CI/CD pipelines.

%--------------------%
%    Experience      %
%--------------------%
\section*{Experience}

\noindent\textbf{Full Stack Engineer at Verior (Part Time)} \hfill \textit{February 2025 - Present} \\

\begin{itemize}[leftmargin=*]
\item \textbf{Certly} – React Native learning \& quiz competition app. \\
\textbf{Role: REST API Integration} \\
Developed and integrated secure REST APIs to handle user authentication, quiz retrieval, and leaderboard synchronization. Optimized data flow between the backend and mobile app to reduce latency and improve reliability. Implemented error handling and data validation to ensure a smooth user experience during quiz attempts. Collaborated closely with backend developers to test, debug, and refine API endpoints for seamless integration and high app performance.

\item \textbf{Opstation} – Logistics \& field management app. \\
\textbf{Role: Front-End Fixes} \\
Contributed to improving the front-end of a logistics and field management platform by resolving critical UI/UX issues. Enhanced responsiveness, fixed layout inconsistencies, and optimized navigation for better usability in real-world field operations. Improved performance by reducing unnecessary re-renders and refactoring components for efficiency. Worked closely with QA and backend teams to ensure a smooth and stable user experience across different devices.
\end{itemize}

\vspace{0.5em} 

\noindent\textbf{Mobile App Developer at Idea To Product} \hfill \textit{June 2024 - January 2025} \\

\begin{itemize}[leftmargin=*]
\item Developed a Full-Stack E-Commerce App utilizing React Native and Firebase. Implemented features allowing admin to post products, manage inventory (add, update, delete products), and receive notifications for new orders.

\item Built a learning App with dual interfaces for parents and children. Parents assign math quizzes based on the child's age and difficulty level. Children earn rewards upon quiz completion, which can be withdrawn as money.
\end{itemize}

\vspace{0.5em} 

\noindent\textbf{Web Developer} \hfill \textit{January 2024 - June 2024} \\

\begin{itemize}[leftmargin=*]
\item \textbf{Make Your Own Meal (USA)} – React Native App. Improved the App's UI to make it user-friendly. Fixed layout issues to ensure compatibility across all devices.

\item Developed responsive web applications using React, TypeScript, and Node.js. Built RESTful APIs, integrated third-party services, and implemented modern UI/UX principles. Created scalable frontend and backend solutions for various client projects.
\end{itemize}

\newpage  % Force page break here so DevOps Engineer starts on a new page

\noindent\textbf{DevOps Engineer} \hfill \textit{April 2024 - January 2025} \\

\begin{itemize}[leftmargin=*]
\item Deployed and maintained backend infrastructure on Amazon EC2 instances. Configured Ubuntu server environments, set up secure SSH access, and managed deployment of backend services using Node.js and PM2.

\item Configured and managed S3 buckets for file storage, implemented Lambda functions for serverless computing, and set up API Gateway for RESTful API management.

\item Set up continuous integration and deployment pipelines. Automated deployment processes, managed Docker containers, and implemented monitoring solutions. Ensured high availability and scalability of cloud-based applications.
\end{itemize}

%--------------------%
%     Projects       %
%--------------------%
\section*{Projects}

\noindent\textbf{One Under App (Mexico)} \hfill \textit{React Native App} \\

\begin{itemize}[leftmargin=*]
    \item Developed a Live Match Betting App using React Native, Supabase \& PowerSync. Enabled real-time sports betting with a responsive UI, offline data access, and background sync for enhanced user experience.
\end{itemize}

\vspace{1ex}

\noindent\textbf{Make Your Own Meal (USA)} \hfill \textit{React Native App} \\

\begin{itemize}[leftmargin=*]
    \item Improved the App's UI to make it user-friendly. Fixed layout issues to make it compatible among all devices.
    \item Deployed and maintained the backend infrastructure on an Amazon EC2 instance. Configured Ubuntu server environment, set up secure SSH access, and managed deployment of backend services using Node.js and PM2.
\end{itemize}

\vspace{1ex}

\noindent\textbf{Cluster Route (USA)} \hfill \textit{React Native App} \\

\begin{itemize}[leftmargin=*]
    \item Developed Admin and Engineer Panels using Firebase. Integrated KML route mapping and real-time progress updates with Google Maps.
\end{itemize}

%--------------------%
%      Skills        %
%--------------------%
\vspace{3ex}
\section*{Skills}

\textbf{Frontend Development:}
\begin{itemize}[leftmargin=*]
    \item React, React Native, JavaScript, TypeScript, Redux, Expo
    \item HTML5, CSS3, SASS, Firebase, Supabase
\end{itemize}

\textbf{Backend Development:}
\begin{itemize}[leftmargin=*]
    \item Node.js, REST APIs, Express, PM2
    \item MySQL, PostgreSQL, MongoDB
    \item Git, GitHub, Postman
\end{itemize}

\textbf{Cloud \& DevOps:}
\begin{itemize}[leftmargin=*]
    \item AWS (EC2, S3, Lambda, API Gateway), Ubuntu, Linux
    \item SSH, Docker, CI/CD
\end{itemize}

%--------------------%
%     Education      %
%--------------------%
\section*{Education}

\noindent\textbf{B.E. in Computer System Engineering} \\
Mehran University of Engineering and Technology, Jamshoro 2021- 2025 (Final Semester)

\vspace{1ex}

\noindent\textbf{Intermediate} \\
Govt Islamia Science and Arts College, Sukkur

%--------------------%
%      Tools         %
%--------------------%
\section*{Tools}
\begin{multicols}{2}
\begin{itemize}[leftmargin=*]
    \item Android Studio
    \item Visual Studio Code
    \item Virtual Device Emulator
    \item MySQL Workbench
\end{itemize}
\end{multicols}

%--------------------%
%      Awards        %
%--------------------%
\section*{Awards}
\begin{itemize}[leftmargin=*]
    \item PEEF Scholarship Awarded
    \item Hacktoberfest 2022 Winner
\end{itemize}

\end{document}
